Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-08-26 paper.tex
implemented Peng's changes

\begin{abstract}
  About one third of X-ray-luminous clusters show smooth, unpolarised radio
  emission on $\sim$Mpc scales, known as giant radio haloes. One promising model
  for radio haloes is Fermi II acceleration of seed relativistic electrons by
  compressible turbulence in the intracluster medium (ICM). The origin of these
  seed electrons has never been fully explored. Here, we integrate the
  Fokker-Planck equation of the cosmic ray (CR) electron and proton
  distributions in \AP{the post-processing of} cosmological simulations of cluster formation, and confront
  them with radio surface brightness and spectral observations of Coma. For
  standard assumptions, structure formation shocks lead to a seed electron
  population which produces too centrally concentrated radio emission. By
  modifying properties of the CR population (rapid streaming; enhanced CR
  electron acceleration at shocks) or turbulence (increasing
  turbulent-to-thermal energy density with radius), we can match observations,
  but only at the expense of fine-tuning. We then perform a parameter
  study. Under naive assumptions, radio properties are exponentially sensitive
  to the amplitude of turbulence, which is inconsistent with small scatter in
  scaling relations. This sensitivity can be removed if we relate the
  acceleration time to the turbulent dissipation time. Their ratio depends only
  on plasma parameters. In this case, turbulence above a threshold value
  required to overcome cooling provides a fixed amount of amplification;
  observations could then potentially constrain the unknown CR seed
  population. Understanding the small scatter in radio halo scaling relations
  may prove a rich source of insight on plasma processes in the ICM.
\end{abstract}

@@

It is important to realise that this Kraichnan scaling only applies at small scales, where turbulence is magneto-hydrodynamical. At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$). Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum. However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent. Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime. The cutoff scale in equation (\ref{eqn:Wk}) can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons. This yields \citep{brunetti07,miniati15}:
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{outer}} \frac{\langle (\delta \varv_{\rmn{outer}})^{2}\rangle^{2}}{c_{\rm s}^{4}}
\label{eqn:k_c1} 
\end{equation}
where $A \approx 11 000$. \cp{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$. However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work, which assumes Kraichnan turbulence from the injection scale onward and effectively adopts wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{A}} \beta^{-2}\,.
\label{eqn:k_c} 
\end{equation}
}
This gives $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}, a possibility we discuss in \S\ref{sect:self-limiting}. Another possibility is that compressible modes dissipate in weak shocks, resulting in Burgers' turbulence $s=2$ \citep{kowal10,porter15,miniati15}. If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio haloes \citep{miniati15}, and an alternative model for radio haloes is required.

@@

What is a typical energy density in compressive fast modes? The total turbulent
energy is typically $\sim 15-70$ per cent of the thermal energy in a cluster
\citep{vazza11}; it rises rapidly during a merger. The compressible component is
$\sim 20-40$ per cent of the total turbulent energy, and shows more rapid temporal
variations compared to the compressible component
\citep{2013ApJ...771..131B,miniati15}. Note the compressible component in
cluster simulations is much larger than in stirring box simulations
with similar Mach numbers \citep{kowal10,lynn14}. This is likely due to the
compressive nature of turbulent driving (transsonic infall and merger), whereas
idealised simulations tend to use incompressible solenoidal driving and allow
compressive fluctuations to develop on their own. Overall, we adopt a
compressive energy density which is $X_{\rm tu} \sim 0.2$ of the thermal energy
as a baseline estimate.

The important effects are best summarised in terms of the acceleration \cp{rate
  which is goverend by advection in momentum space:
\begin{equation}
  \tau_{\rm D}^{-1}\equiv \Gamma_{\rm D}\equiv
  \frac{\dot{p}}{p}=p^{-3}\frac{\partial}{\partial p}\left(p^2D_{pp}\right)
  =\frac{4 D_{pp}}{p^{2}}.
\end{equation}
In the last step we have used that $D_{pp}\propto p^2$ for turbulent
reacceleration (equation \ref{eqn:Dpp}). Hence the acceleration time is independent of momentum.}
%\begin{equation}
%\tau_{\rm D}= \frac{p^{2}}{4 D_{pp}}
%\end{equation}
%which is momentum independent.
This should be compared against the lifetime of turbulence, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}$. In Table~\ref{tab:timescales}, we show both the thermal quantities and the
timescales for CR cooling and (re)acceleration for three different
spatial regions of the RH. The densities \citep{1992A&A...259L..31B} and temperatures \citep{2009ApJ...696.1886B,2001A&A...365L..67A} are derived from X-ray observations. To calculate synchrotron cooling times, we use $B$-fields derived from Faraday rotation measurements \citep{bonafede10}. To calculate the acceleration time, we need to assume an outer scale. We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}. This length scale corresponds to an eddy turnover time on the outer scale of \cp{$2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger. Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \AP{\citep[e.g. $\lambda_L \sim 1 {\rm Mpc}$ in ][]{vazza11,miniati15}}. This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$. We present $\tau_{\rm D}$ for 3 different models, which we discuss in the next section. The reacceleration timescale
$\tau_{\rm D}$ is similar between our three models, where the
difference comes from turbulent profile parametrized with
$\alpha_\rmn{tu}$. This implies that even small differences in the
turbulent profile could impact the seed CRs significantly. Finally, we adopt an duration of acceleration $\tau_{\rm cl} = 650$ Myr, in line with previous assumptions \citep{brunetti07}, roughly corresponding to the turbulent decay time. 
\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_{\rmn{e}}c)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{had}(P=100\,m_{\rmn{p}}c)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{Coul}(P=\,m_{\rmn{e}}c)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a derived 
 during last 300~Myrs in time. \\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_{\rmn{e}}/m_{\rmn{p}}$ smaller).\\
 \label{tab:timescales}
  \end{quote}
\end{table}

@@

@@

We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Figure
\ref{fig:param_comp}; note from equation (\ref{eq:Dpp_scaling}) that $\tau_{\rm D}
\propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
  tu}$ to explain the observations, it is worth understanding this property in
more detail. To this end, we ignore cooling which is a good approximation for
the CR protons, because hadronic cooling times are long in comparison to the
other relevant timescales of the problem.\footnote{In principle, CRp can still
  lose energy via wave heating, at a rate $\left|\bmath{\varv_{\rm A} \cdot
    \nabla} P_\CR\right|$, but we assume CR streaming is suppressed during
  mergers, when they are spatially confined by scattering.} In this case,
$\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p
\rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the
fact that $\tau_{\rm D}$ is momentum independent). For an initial power law
distribution function $f(p) = C p^{-\alpha_{\rmn{inj}}}$, this momentum increase can be
rewritten as a change of normalisation, $f(p) = \tilde{C} p^{-\alpha_{\rmn{inj}}}$, where
$\tilde{C} = {\rm exp}( \alpha_{\rmn{inj}} \tau_{\rm cl}/\tau_{\rm D})$. A slightly more
careful derivation by direct solution of the Fokker-Planck equation yields:
\begin{equation}
  \dot{f} = {{\partial }\over{\partial p}}
  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
\end{equation}
with the analytic solution given by
\cp{
\begin{equation}
  \label{eq:Creacc}
  \tilde{C}= 
  C \exp{\left[\frac{(2+\alpha_{\rmn{inj}})(\alpha_{\rmn{inj}}-1)}{4}\frac{t}{\tau_\rmn{D}}\right]}\,.
\end{equation}
At $t=\tau_\rmn{cl}$} the CR distribution is exponentially sensitive to
$\tau_{\rm cl}/\tau_{\rm D}$ which is the physical reason underlying
the extreme sensitivity to $X_{\rm tu}$ in
Figure~\ref{fig:param_comp}.

@@

An obvious candidate for $\tau_{\rm decay}$ is: 
\begin{equation}
\tau_{\rm edd} = \frac{L}{\varv_{\rm c}}
\end{equation}
i.e., the eddy turnover time at the outer scale. This is subject to
uncertainties about the location of the outer scale $L$; estimates in the
literature range from $L \sim 0.1-1$ Mpc. It is also worth remembering that MHD
turbulence only applies for $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n
scale where $\varv \sim \varv_{\rm A}$. Invoking fast modes, Kraichnan scalings,
etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
basically hydrodynamic and follows the universal Kolmogorov scaling. The
momentum diffusion coefficient can thus be split up into two components:
\begin{equation}
D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
\end{equation}
From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
\begin{equation}
  \label{eqn:Dratio}
  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
  = \cp{2} A^{-1/2} \beta = \cp{1.0}\, \left( \frac{\beta}{50} \right) 
\end{equation}
where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov
scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the
Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm
  s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation
\ref{eqn:k_c}).  Thus, the contribution of the two regimes are
comparable\footnote{\cp{The estimate of equation~(\ref{eqn:Dratio}) assumes that
    in both cascades, kinetic and potential energy are in equipartition which is
    likely an overestimate for the hydrodynamical cascade and hence, the
    hydrodynamic contribution to the momentum diffusion would be small in
    comparison to the MHD contribution. }} (as we shall see later, this is not
true if one incorrectly assumes Kraichnan scalings apply from the outer scale
$L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a
factor $\mathcal{M}_{\rm A}^{1/2}$).

>>>>

\begin{abstract}
  About one third of X-ray-luminous clusters show smooth, unpolarised radio
  emission on $\sim$Mpc scales, known as giant radio haloes. One promising model
  for radio haloes is Fermi II acceleration of seed relativistic electrons by
  compressible turbulence in the intracluster medium (ICM). The origin of these
  seed electrons has never been fully explored. Here, we integrate the
  Fokker-Planck equation of the cosmic ray (CR) electron and proton
  distributions in \AP{the post-processing of} cosmological simulations of cluster formation, and confront
  them with radio surface brightness and spectral observations of Coma. For
  standard assumptions, structure formation shocks lead to a seed electron
  population which produces too centrally concentrated radio emission. By
  modifying properties of the CR population (rapid streaming; enhanced CR
  electron acceleration at shocks) or turbulence (increasing
  turbulent-to-thermal energy density with radius), we can match observations,
  but only at the expense of fine-tuning. We then perform a parameter
  study. Under naive assumptions, radio properties are exponentially sensitive
  to the amplitude of turbulence, which is inconsistent with small scatter in
  scaling relations. This sensitivity can be removed if we relate the
  acceleration time to the turbulent dissipation time. Their ratio depends only
  on plasma parameters. In this case, turbulence above a threshold value
  required to overcome cooling provides a fixed amount of amplification;
  observations could then potentially constrain the unknown CR seed
  population. \po{Given that MHD turbulence only begins at the Alfven scale, in order to have sufficient acceleration, the turbulent cascade has to terminate by transit time damping on CRs, i.e., thermal particles must be scattered by plasma instabilities.} Understanding the small scatter in radio halo scaling relations
  may prove a rich source of insight on plasma processes in the ICM.
\end{abstract}

@@

It is important to realise that this Kraichnan scaling only applies at small scales, where turbulence is magneto-hydrodynamical. At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$). Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum. However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density \po{(which is dominated by the large scale mean field} is scale-independent. Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime. The cutoff scale in equation (\ref{eqn:Wk}) can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons. This yields \citep{brunetti07,miniati15}:
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{outer}} \frac{\langle (\delta \varv_{\rmn{outer}})^{2}\rangle^{2}}{c_{\rm s}^{4}}
\label{eqn:k_c1} 
\end{equation}
where $A \approx 11 000$. \cp{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$. However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work, which assumes Kraichnan turbulence from the injection scale onward and effectively adopts wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{A}} \beta^{-2}\,.
\label{eqn:k_c} 
\end{equation}
}
This gives $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}, a possibility we discuss in \S\ref{sect:self-limiting}. Another possibility is that compressible modes dissipate in weak shocks, resulting in Burgers' turbulence $s=2$ \citep{kowal10,porter15,miniati15}. If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio haloes \citep{miniati15}, and an alternative model for radio haloes is required.

@@

What is a typical energy density in compressive fast modes? The total turbulent
energy is typically $\sim 15-70$ per cent of the thermal energy in a cluster
\citep{vazza11}; it rises rapidly during a merger. The compressible component is
$\sim 20-40$ per cent of the total turbulent energy, and shows more rapid temporal
variations compared to the \po{incompressible} component
\citep{2013ApJ...771..131B,miniati15}. Note the compressible component in
cluster simulations is much larger than in stirring box simulations
with similar Mach numbers \citep{kowal10,lynn14}. This is likely due to the
compressive nature of turbulent driving (transsonic infall and merger), whereas
idealised simulations tend to use incompressible solenoidal driving and allow
compressive fluctuations to develop on their own. Overall, we adopt a
compressive energy density which is $X_{\rm tu} \sim 0.2$ of the thermal energy
as a baseline estimate.

The important effects are best summarised in terms of the acceleration \cp{rate
  which is governed by advection in momentum space:
\begin{equation}
  \tau_{\rm D}^{-1}\equiv \Gamma_{\rm D}\equiv
  \frac{\dot{p}}{p}=p^{-3}\frac{\partial}{\partial p}\left(p^2D_{pp}\right)
  =\frac{4 D_{pp}}{p^{2}}.
\end{equation}
In the last step we have used that $D_{pp}\propto p^2$ for turbulent
reacceleration (equation \ref{eqn:Dpp}). Hence the acceleration time is independent of momentum.}
%\begin{equation}
%\tau_{\rm D}= \frac{p^{2}}{4 D_{pp}}
%\end{equation}
%which is momentum independent.
This should be compared against the lifetime of turbulence, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}$. In Table~\ref{tab:timescales}, we show both the thermal quantities and the
timescales for CR cooling and (re)acceleration for three different
spatial regions of the RH. The densities \citep{1992A&A...259L..31B} and temperatures \citep{2009ApJ...696.1886B,2001A&A...365L..67A} are derived from X-ray observations. To calculate synchrotron cooling times, we use $B$-fields derived from Faraday rotation measurements \citep{bonafede10}. To calculate the acceleration time, we need to assume an outer scale. We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}. This length scale corresponds to an eddy turnover time on the outer scale of \cp{$2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger. Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \AP{\citep[e.g. $\lambda_L \sim 1 {\rm Mpc}$ in ][]{vazza11,miniati15}}. This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$. We present $\tau_{\rm D}$ for 3 different models, which we discuss in the next section. The reacceleration timescale
$\tau_{\rm D}$ is similar between our three models, where the
difference comes from turbulent profile parametrized with
$\alpha_\rmn{tu}$. This implies that even small differences in the
turbulent profile could impact the seed CRs significantly. Finally, we adopt an duration of acceleration $\tau_{\rm cl} = 650$ Myr, in line with previous assumptions \citep{brunetti07}, roughly corresponding to the turbulent decay time. 
\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_{\rmn{e}}c)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{had}(P=100\,m_{\rmn{p}}c)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{Coul}(P=\,m_{\rmn{e}}c)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a derived 
 during last 300~Myrs in time. \\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_{\rmn{e}}/m_{\rmn{p}}$ smaller).\\
 \label{tab:timescales}
  \end{quote}
\end{table}

@@

\po{In this section, we explore the physical origin of the high sensitivity of radio emission to turbulence levels (e.g., top right panel of Fig. \ref{fig:param_comp}), which thus requires strong fine-tuning to explain observed radio profiles. We will find that by relating the acceleration time to the turbulent decay time, this sensitivity can be eliminated.  We also challenge the common assumption of assuming a Kraichnan spectrum, beginning at the outer scale (see \S\ref{sec:reacc}). Since turbulence is essentially hydrodynamic at large scales, this is unjustified. Instead, we shall assume that the outer scale of the compressive fast modes is the Alfven scale.}

@@

We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Figure
\ref{fig:param_comp}; note from equation (\ref{eq:Dpp_scaling}) that $\tau_{\rm D}
\propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
  tu}$ to explain the observations, it is worth understanding this property in
more detail. To this end, we ignore cooling, which is a good approximation for
the CR protons, because hadronic cooling times are long in comparison to the
other relevant timescales of the problem.\footnote{In principle, CRp can still
  lose energy via wave heating, at a rate $\left|\bmath{\varv_{\rm A} \cdot
    \nabla} P_\CR\right|$, but we assume CR streaming is suppressed during
  mergers, when they are spatially confined by scattering.} In this case,
$\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p
\rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the
fact that $\tau_{\rm D}$ is momentum independent). For an initial power law
distribution function $f(p) = C p^{-\alpha_{\rmn{inj}}}$, this momentum increase can be
rewritten as a change of normalisation, $f(p) = \tilde{C} p^{-\alpha_{\rmn{inj}}}$, where
$\tilde{C} = {\rm exp}( \alpha_{\rmn{inj}} \tau_{\rm cl}/\tau_{\rm D})$. A slightly more
careful derivation by direct solution of the Fokker-Planck equation yields:
\begin{equation}
  \dot{f} = {{\partial }\over{\partial p}}
  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
\end{equation}
with the analytic solution given by
\cp{
\begin{equation}
  \label{eq:Creacc}
  \tilde{C}= 
  C \exp{\left[\frac{(2+\alpha_{\rmn{inj}})(\alpha_{\rmn{inj}}-1)}{4}\frac{t}{\tau_\rmn{D}}\right]}\,.
\end{equation}
At $t=\tau_\rmn{cl}$} the CR distribution is exponentially sensitive to
$\tau_{\rm cl}/\tau_{\rm D}$, which is the physical reason underlying
the extreme sensitivity to $X_{\rm tu}$ in
Figure~\ref{fig:param_comp}.

@@

An obvious candidate for $\tau_{\rm decay}$ is: 
\po{\begin{equation}
\tau_{\rm edd} = \frac{L}{\varv_{\rm L}}
\end{equation}}
i.e., the eddy turnover time at the outer scale. This is subject to
uncertainties about the location of the outer scale $L$; estimates in the
literature range from $L \sim 0.1-1$ Mpc. It is also worth remembering that MHD
turbulence only applies for $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n
scale where $\varv \sim \varv_{\rm A}$. Invoking fast modes, Kraichnan scalings,
etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
basically hydrodynamic.

\po{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolomogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}. The Burgers-like component does not reflect a genuine cascade, but rather the appearance of shocks which directly transfer power from large to small scales. At face value, we should use the Burgers spectrum for compressible modes. However, as already found by previous authors \citep{miniati15, brunetti16}, and as we shall discuss, this does not produce significant particle acceleration. If this is the correct spectrum, then the paradigm of turbulent particle acceleration is simply flawed, and some other mechanism is necessary to explain radio halos. Alternatively, it is well-known that due to mode-mode coupling,  solenoidal modes can give rise to compressive modes, and vice-versa \citep{kida90,cho03,kritsuk07}, even for subsonic turbulence, since pressure fluctuations of order $\sim \rho u^{2}$ arise. Indeed, note that many numerical studies (such as \citet{cho03,kritsuk07}) only have solenoidal driving on the outer scale, but then are also able to study the compressive modes that develop. In hydrodynamic turbulence, the energy in compressible modes which develop in this way scales as $\sim \mathcal{M}_{s}^2$, for $\mathcal{M}_{s} < 1$; this coupling is strongest at the Alfven scale \citep{cho03}. In MHD turbulence, mode-mode coupling is weak below the Alfven scale and the Alfven, fast and slow modes proceed as separate cascades.}

\po{We thus assume that some fraction of the Kolmogorov-like hydrodynamic turbulence which cascades down to the Alfven scale ends up as compressive fast modes with a Kraichnan spectrum, as seen in simulations \citep{cho03}. Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$. If some fraction $f_{\rm c}$ of the turbulent energy density at this scale is in compressible modes, then the energy density at the outer scale is velocity $\sim f_{\rm c} \rho \varv_{\rm A}^{2}$.}
%and follows the universal Kolmogorov scaling. The
%momentum diffusion coefficient can thus be split up into two components:
%\begin{equation}
%D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
%\end{equation}
%From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
%\begin{equation}
%  \label{eqn:Dratio}
%  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
%  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
%  = \cp{2} A^{-1/2} \beta = \cp{1.0}\, \left( \frac{\beta}{50} \right) 
%\end{equation}
%where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov
%scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the
%Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm
%  s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation
%\ref{eqn:k_c}).  Thus, the contribution of the two regimes are
%comparable\footnote{\cp{The estimate of equation~(\ref{eqn:Dratio}) assumes that
%%    in both cascades, kinetic and potential energy are in equipartition which is
%    likely an overestimate for the hydrodynamical cascade and hence, the
%   hydrodynamic contribution to the momentum diffusion would be small in
%    comparison to the MHD contribution. }} (as we shall see later, this is not
%true if one incorrectly assumes Kraichnan scalings apply from the outer scale
%$L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a
%factor $\mathcal{M}_{\rm A}^{1/2}$).
The turbulent reacceleration time is: 
%\begin{equation}
%\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
%\label{eqn:tau_D} 
%\end{equation}
\po{
  \begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \po{\frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{\beta}{f_{\rm c} \varv_{\rm A}^{2}}}
\label{eqn:tau_D} 
\end{equation}
}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equations, \po{(\ref{eqn:diffusion}), (\ref{eqn:k_W}), (\ref{eqn:k_c}), assuming $s=3/2$}. The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}): 
\begin{equation}
  \tau_{\rm decay} = \cp{\frac{\varv_{\rm ph}}{\varv_k^{2} k} = }
\po{\frac{c_{\rm s}}{f_{\rm c} \varv_{\rm A}^{2} k_{\rm A}^{}}\,.}
\label{eqn:tau_decay} 
\end{equation}
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\po{\tau_{\rm decay} =\frac{L}{\varv_{\rm L}} \frac{c_{\rm s}^{2}}{f_{\rm c} \varv_{\rm L}^{2}}  \frac{\varv_{\rm A}}{c_{\rm s}} \approx  1.0 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{50} \right)^{-1/2}}
\end{equation}
where we have used $\tilde{X}_{\rm tu} \approx f_{\rm c} (\varv_{\rm L}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. \po{The decay time at the Alfven scale is comparable (and could be larger, if $f_{\rm c}$ is smaller than we have assumed) to the eddy turnover time at the outer scale. Thus, it is appropriate to consider the latter as the decay time for the fast modes, rather than the cascade time at the driving scale. The reason for these comparable timescales despite the disparate lengthscales is that large scale hydrodynamic modes cascade on a single eddy turnover time, whereas small scale sub-Alfvenic MHD modes are in the weak turbulence limit, and require multiple wave-wave interactions for a mode to cascade.  }
